LAGOS lake depth

### 2020-02-06 figures/01_contrasts.Rmd
expand y axes

```{r gg_tally_programtype, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# tally number of lakes with max depth by programtype_depth
gg_tally_programtype <- read.csv(
  "../data/lagosus_depth.csv", stringsAsFactors = FALSE) %>% 
   dplyr::filter(!is.na(lake_maxdepth_m)) %>%
   group_by(programtype_depth) %>% 
   tally() %>% 
   ggplot(aes(x = programtype_depth, y = n)) + 
   geom_col() + 
   geom_text(aes(label = n), vjust = -0.5) + 
   ylim(0, 11000) +
  xlab("Program type")
```

@@

```{r gg_tally_waterareaclass, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# panel histograms that tally number of lakes with max depth by waterarea_class
# include sum across all types
gg_tally_waterareaclass <- read.csv("../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  mutate(area_class =
           smart_cut(lake_waterarea_ha, c(1, 4, 40, 80, 300, 400,
                                               1000, 20000, Inf),
             labels = ~paste(sep="-", thousand_k(.y[1]), thousand_k(.y[2])))
         ) %>%
  group_by(area_class) %>%
  tally() %>%
  ggplot(aes(x = area_class, y = n)) +
  geom_col() + 
  geom_text(aes(label = n), vjust = -0.5) +
  ylim(0, 10000) + 
  xlab("Lake area class (ha)")
```

```{r gg_tally_hypsoclass, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
gg_tally_hypsoclass <- read.csv(
  "../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  distinct(lagoslakeid, shape_class, .keep_all = TRUE) %>%
  group_by(shape_class) %>%
  tally() %>%
  ggplot(aes(x = shape_class, y = n)) +
  geom_col() + 
  geom_text(aes(label = n), vjust = -0.5) +
  ylim(0, 3000) + 
  xlab("Shape class")
```

>>>>

```{r gg_tally_programtype, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# tally number of lakes with max depth by programtype_depth
gg_tally_programtype <- read.csv(
  "../data/lagosus_depth.csv", stringsAsFactors = FALSE) %>% 
   dplyr::filter(!is.na(lake_maxdepth_m)) %>%
   group_by(programtype_depth) %>% 
   tally() %>% 
   ggplot(aes(x = programtype_depth, y = n)) + 
   geom_col() + 
   geom_text(aes(label = n), vjust = -0.5) + 
   ylim(0, 13000) +
  xlab("Program type")
```

@@

```{r gg_tally_waterareaclass, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# panel histograms that tally number of lakes with max depth by waterarea_class
# include sum across all types
gg_tally_waterareaclass <- read.csv("../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  mutate(area_class =
           smart_cut(lake_waterarea_ha, c(1, 4, 40, 80, 300, 400,
                                               1000, 20000, Inf),
             labels = ~paste(sep="-", thousand_k(.y[1]), thousand_k(.y[2])))
         ) %>%
  group_by(area_class) %>%
  tally() %>%
  ggplot(aes(x = area_class, y = n)) +
  geom_col() + 
  geom_text(aes(label = n), vjust = -0.5) +
  ylim(0, 11000) + 
  xlab("Lake area class (ha)")
```

```{r gg_tally_hypsoclass, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
gg_tally_hypsoclass <- read.csv(
  "../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  distinct(lagoslakeid, shape_class, .keep_all = TRUE) %>%
  group_by(shape_class) %>%
  tally() %>%
  ggplot(aes(x = shape_class, y = n)) +
  geom_col() + 
  geom_text(aes(label = n), vjust = -0.5) +
  ylim(0, 4500) + 
  xlab("Shape class")
```
